\begin{thebibliography}{} % Máximo de referencias
	
	\bibitem[AnDev]{AnDev}
	Portal de Android Developers en
	\emph{\url{https://developer.android.com}}.
	
	\bibitem[Arl02]{Arl02} 
	Arlow, J. y I. Neustadt, 
	\emph{UML and the Unified Process}, 
	Addison-Wesley, 
	2002.
	
	\bibitem[Bas03]{Bas03} 
	Bass, L., P. Clements y R. Kazman, 
	\emph{Software Architecture in Practice}, 
	2a. ed., 
	Addison-Wesley, 
	2003.
	
	\bibitem[Bei90]{Bei90} 
	Beizer, B., 
	\emph{Software Testing Techniques}, 
	2a. ed., 
	Van Nostrand-Reinhold, 
	1990.

	\bibitem[Coa91]{Coa91} 
	Coad, P. y E. Yourdon, 
	\emph{Object-Oriented Analysis}, 
	2a. ed., 
	Prentice Hall, 
	1991.
	
	\bibitem[Coo00]{Coo00} 
	Cooper, J. W.,
	\emph{Java Design Patterns: A Tutorial}, 
	Addison-Wesley Professional, 
	2000.
	
	\bibitem[DocOr]{DocOr}
	Portal de documentación técnica Oracle sobre Java en
	\emph{\url{http://docs.oracle.com/javase}}.
	
	\bibitem[EckPa]{EckPa} 
	Eckel, B.
	\emph{Thinking in Patterns}.
	
	\bibitem[Gar87]{Gar87}
	Garvin D.,
	\emph{Competing on the Eight Dimensions of Quality},
	Harvard Business Review, 
	noviembre 1987.
	
	\bibitem[GF13]{GF13}
	\emph{GlassFish Server Open Source Edition - Quick Start Guide},
	4.0,
	2013.
	
	\bibitem[IE830]{IE830}
	Institute of Electrical and Electronics Engineers (IEEE),
	\emph{IEEE Std. 830-1998: Especificaciones de los Requisitos del Software}.
	
	\bibitem[ISO25]{ISO25}
	International Organization for Standardization (ISO),
	\emph{ISO/IEC 25010:2011 - Systems and software engineering - Systems and software Quality Requirements and Evaluation (SQuaRE) - System and software quality models}.
	
	\bibitem[JSON]{JSON}
	``Introducción a JSON'' en
	\emph{\url{http://www.json.org/json-es.html}}.
	
	\bibitem[Kan99]{Kan99}
	Kaner, C., J. Falk y H. Q. Nguyen,
	\emph{Testing Computer Software},
	2a. Rev. ed.,
	John Wiley \& Sons, 
	1999.
	
	\bibitem[Man97]{Man97}
	Mandel, T.,
	\emph{The Elements of User Interface Design},
	John Wiley \& Sons, 
	1997.
		
	\bibitem[McC77]{McC77}
	McCall, J., P. Richards y G. Walters,
	\emph{Factors in Software Quality, Volume I. Concepts and Definitions of Software Quality}, 
	1977.

	\bibitem[Mye11]{Mye11}
	Myers, G., C. Sandler, y T. Badgett,
	\emph{The Art of Software Testing},
	3a. ed.,
	John Wiley \& Sons, 
	2011.
	
	\bibitem[NetRF]{NetRF}
	``Getting Started with RESTful Web Services'' en
	\emph{\url{https://netbeans.org/kb/docs/websvc/rest.html}}.
	
	\bibitem[Oet15]{Oet15}
	Oetiker T. et al,
	\emph{The Not So Short Introduction to \LaTeXe},
	5.05,
	2015.
	
	\bibitem[OraDB]{OraDB}
	``Java SE Technologies - Database'' en	
	\emph{\url{http://www.oracle.com/technetwork/java/javase/jdbc/index.html}}.
	
	\bibitem[OraEE]{OraEE}
	``Java EE at a Glance'' en
	\emph{\url{http://www.oracle.com/technetwork/java/javaee/overview/index.html}}.
	
	\bibitem[Pre10]{Pre10}
	Pressman, R. S.,
	\emph{Ingeniería del software: un enfoque práctico},
	7a. ed.,
	McGrawHill,
	2010.
	
	\bibitem[Sha96]{Sha96} 
	Shaw, M. y D. Garlan, 
	\emph{Software Architecture}, 
	Prentice Hall, 
	1996.
	
	\bibitem[WREST]{WREST}
	``Representational state transfer'' en
	\emph{\url{https://en.wikipedia.org/wiki/Representational_state_transfer}}.
	
	\bibitem[WSOAP]{WSOAP}
	``SOAP'' en
	\emph{\url{https://en.wikipedia.org/wiki/SOAP}}.
	
	\bibitem[WWSer]{WWSer}
	``Web Service'' en
	\emph{\url{https://en.wikipedia.org/wiki/Web_service}}.

\end{thebibliography}